From Freebase to Wikidata: The Great Migration

### 2015-10-15 paper.tex
Added Lydia. Some minor corrections in abstract.

\numberofauthors{3}
\author{
Thomas Pellissier Tanon,\titlenote{The author was an intern at Google when the majority of the work was done.} Denny Vrandečić\\
   \affaddr{Google San Francisco, United States of America}\\   
   \email{\{thomaspt, vrandecic\}@google.com}
\alignauthor
Sebastian Schaffert\\
   \affaddr{Google Zurich, Switzerland}\\   
   \email{schaffert@google.com}
\alignauthor
Thomas Steiner\\
   \affaddr{Google Hamburg, Germany}\\   
   \email{tsteiner@google.com}
}

\begin{document}

@@

\begin{abstract}
Collaborative knowledge bases that make their data freely available in a machine-readable form
are central for the data strategy of many projects and organizations.
One such collaborative knowledge base is Freebase,
initially launched by Metaweb in 2007.
Metaweb was acquired by Google in 2010.
Another example is Wikidata,
a~collaborative knowledge base developed by Wikimedia Deutschland since 2012
and operated by the Wikimedia Foundation.
Due to the success of Wikidata, Google decided 2015 to shut down Freebase and
help the community with the transfer of Freebase's content to Wikidata.
In this paper, we describe the ongoing transfer efforts and data mapping challenges,
and provide an analysis of the effort so far.
We have created the \emph{Primary Sources Tool}
that we have released as open source to facilitate the transfer of this dataset,
but also future data migrations.
Throughout the migration, we have gained insights into both Wikidata and Freebase,
and share and discuss detailed statistics on both knowledge bases. 
\end{abstract}

>>>>

\numberofauthors{5}
\author{
\alignauthor
Thomas Pellissier Tanon\titlenote{The author was an intern at Google when the majority of the work was done.}
   \affaddr{Google, San Francisco, USA}\\   
   \email{thomaspelta@gmail.com}
\alignauthor
Denny Vrandečić
   \affaddr{Google, San Francisco, USA}\\   
   \email{vrandecic@google.com}
\alignauthor
Sebastian Schaffert\\
   \affaddr{Google, Zurich, Switzerland}\\   
   \email{schaffert@google.com}
\and
\alignauthor
Thomas Steiner\\
   \affaddr{Google, Hamburg, Germany}\\   
   \email{tomac@google.com}
\alignauthor
Lydia Pintscher\\
   \affaddr{Wikimedia, Berlin, Germany}\\   
   \email{mail@pintscher.de}
}
\begin{document}

@@

\begin{abstract}
Collaborative knowledge bases that make their data freely available in a~machine-readable form
are central for the data strategy of many projects and organizations.
One such collaborative knowledge base is Freebase, initially launched by Metaweb in 2007,
who were then acquired by Google in 2010.
Another example is Wikidata, a~collaborative knowledge base developed by
Wikimedia Deutschland since 2012 and operated by the Wikimedia Foundation.
Due to the success of Wikidata, Google decided 2015 to shut down Freebase and
help the community with the transfer of Freebase's content to Wikidata.
In this paper, we describe the ongoing transfer efforts and data mapping challenges,
and provide an analysis of the effort so far.
We have created the \emph{Primary Sources Tool}
that we have released as open source to facilitate the transfer of this dataset,
but also future data migrations.
Throughout the migration, we have gained insights into both Wikidata and Freebase,
and share and discuss detailed statistics on both knowledge bases. 
\end{abstract}
